HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2022-01-18 hermes_paper/hermes_ieee.tex
update the m4 dataset appendix part

%Looking at the final result of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset. Except one approach, all of them are a combination of different models in order to increase the robustness of the final forecast and at the same time achieve a better global accuracy. The remaining one is not an ensembling but a statistical framework called \textit{Forecast Pro}. It is not a single statistical model but a framework that chooses, depending on the sequence properties, the best statistical approach. With a OWA equal to 0.739, it outperforms the \textit{hermer-tbats} and all the M4 proposed models on the M4 weekly sub-dataset. A description and interesting remarks about the \textit{Forecast Pro} model are discussed in \cite{DARIN2020135}. This model offers an interesting research perspective specifically for the M4 weekly forecasting task.
Looking at the final result of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset. All of them are ensemble framework : a combination of different models in order to increase the robustness of the final forecast and the global accuracy. If this paper, only individual models were compared on the fashion dataset and on the M4 dataset. However, the HERMES framework, as any individual method, is perfectly suited to be include in an ensembling model like the FFORMA approach proposed in \cite{MONTEROMANSO202086}.

>>>>

%Looking at the final result of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset. Except one approach, all of them are a combination of different models in order to increase the robustness of the final forecast and at the same time achieve a better global accuracy. The remaining one is not an ensembling but a statistical framework called \textit{Forecast Pro}. It is not a single statistical model but a framework that chooses, depending on the sequence properties, the best statistical approach. With a OWA equal to 0.739, it outperforms the \textit{hermer-tbats} and all the M4 proposed models on the M4 weekly sub-dataset. A description and interesting remarks about the \textit{Forecast Pro} model are discussed in \cite{DARIN2020135}. This model offers an interesting research perspective specifically for the M4 weekly forecasting task.
Looking at the final results of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset. All of them are ensemble frameworks: methods that mix different kinds of approaches to reach a higher final accuracy. As the M4 weekly dataset gathers really heterogeneous sequences, combining several methods to leverage their strengths appear to be a promising way. However in this paper, only individual models were evaluated in order to provide a fair comparison with the HERMES framework.
